%!TEX root = paper.tex

\section{Introduction}
%\vspace{-2pt}

% problem context
Cloud computing is a technology where resources like storage, infrastructure, softwares, etc are made available on demand  over the network or the Internet. Thus, network is an essential component of cloud computing. With explosive growth of Internet and developement of other computing technologies, the use of cloud resources has also been tremendously increased. Cloud computing is providing a flexible, on-demand, and dynamically scalable computing infrastructure for many applications \cite{furht2010handbook}. With its major services including software-as-a-service, infracture-as-a-service, and platform-as-a-service, cloud computing is advancing the information technology processes and the IT marketplace.  Cloud computing actually is a specialized distributed computing 
technique which provides features such as massive scalability, dynamically configured services (e.g. via virtualization) and delivered on-demand. 

Several studies have shown that billions of dollars have been spent on cloud services worldwide \cite{moura2016review}. This scenario raises a plethora of challanges that are directly related with the networks and communication technologies being used in cloud solutions. For example, virtualization is a crucial technology behind the success of cloud computing but it creates several networking challanges \cite{mishra2012cloud}. Some general challanges associated directly and indirectly with network and communication aspects of growing cloud are lack of trust and privacy, and QoS (Quality of Service) control. Several studies have been done regarding the network related challanges in utilizing cloud services\cite{azodolmolky2013cloud}. As in the other areas of computing, security remains one the major challange. Because of remote access of infrastructure and services, privacy is also an important concern for cloud users\cite{takabi2010security}.

This paper presents an insight into the past and present issues in networking and communication for clouds as well as emerging issues in the future in an attempt to provide a comprehensive assessment of technologies that have been proposed for the solutions.   

% existing works and insufficiencies 

% our work: its strength, how and why it works, results summary


% summary of contributions

The key expected contributions of this paper can be summarized as follows:
\vspace{-2pt}
\begin{itemize}
 \denseitems
 \item 
 Provide a concise summary of challanges in cloud computing with a focus on network and communication
 \item 
 Empirical evaluation of existing solutions to cloud network related challanges
\item 
Identify open and emerging issues related to cloud networks
 \item 
 Propose possible solutions to open and emerging issues related to networking and communication in cloud.
 
\end{itemize}
%\vspace{6pt}
